weight_analyses

### 2023-03-20 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
Added some summary stats and fixed FL label

Mean
```{r}
Cage_only_RVR %>%
  summarize(meanWtPre = mean(Pre_Weight_g),
            meanWtPost = mean(Post_Weight_g),
            meandeltaWt = mean(deltaWt),
            n = n(),
            sddeltaWt = sd(deltaWt),
            sedeltaWt = sddeltaWt/n,
            meanchangeWt = mean(changeWt*100),
            sdchangeWt = sd(changeWt),
            sechangeWt = sdchangeWt/n,
            meanchangeFL =mean(changeFL*100),
            sechangeFL = sd(changeFL)/n,
            meanCFPre = mean(Pre_CF),
            meanCFPost = mean(Post_CF),
            seCF = sd(Pre_CF)/n,
            meandeltaCF = mean(Delta_CF),
            sedeltaCF = sd(Delta_CF)/n)
```

@@

Summary Stats
```{r}
Cage_only_DWSC %>%
  summarize(meanWtPre = mean(Pre_Weight_g),
            meanWtPost = mean(Post_Weight_g),
            meandeltaWt = mean(deltaWt),
            n = n(),
            sddeltaWt = sd(deltaWt),
            sedeltaWt = sddeltaWt/n,
            meanchangeWt = mean(changeWt*100),
            sdchangeWt = sd(changeWt),
            sechangeWt = sdchangeWt/n,
            meanchangeFL =mean(changeFL*100),
            sechangeFL = sd(changeFL)/n,
            meanCFPre = mean(Pre_CF),
            meanCFPost = mean(Post_CF),
            seCF = sd(Pre_CF)/n,
            meandeltaCF = mean(Delta_CF),
            sedeltaCF = sd(Delta_CF)/n)
```

@@

Make length plot
```{r}
CagePrePost <- gather(Cageonly2, PrePost,Length1,Pre_FL_cm, Post_FL_cm)
CagePrePost$Site <- factor(CagePrePost$Site, levels = c("RV", "DWSC"))

MeanLengthplot<- ggplot(data=CagePrePost) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=Length1,  fill = PrePost)) +
  facet_wrap(~Site) +
  labs(y = "Length (cm)") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)++
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "", labels = c("Pre-Deployment", "Post-Deployment")) +
  labs(y = "Length (cm)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
  theme_minimal() + theme(axis.title.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
  #scale_fill_discrete(name = "", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanLengthplot
```

@@

MeanWeightplot<- ggplot(data=CagePrePostW) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=Weight1,  fill = PrePostW)) +
  facet_wrap(~Site) +
  labs(y = "Mean Weight (g)") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)+
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment"))+
  #palette="Dark2" 
   labs(y = "Weight (g)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
  theme_minimal() + theme(strip.text.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) + 
  #scale_fill_discrete(name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        axis.text = element_text(size = 16),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanWeightplot
```

@@

MeanKplot<- ggplot(data=CagePrePostK) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=K1,  fill = PrePostK)) +
  facet_wrap(~Site) +
  labs(y = "Mean K") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)+
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment"))+
  #palette="Dark2" 
   labs(y = expression(K~(g~cm^-3)), x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
  theme_minimal() + theme(strip.text.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) + 
  #scale_fill_discrete(name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanKplot
```

@@

Export
```{r}
tiff(filename=file.path("smelt_2019_winterspring/figures/WeightLengthKPlot.tiff"), units="in",type="cairo", bg="white", height=7, 
     width=7, res=300, pointsize=12,compression="lzw")
lwkplot
dev.off()
```

>>>>

Mean
```{r}
Cage_only_RVR %>%
  summarize(meanWtPre = mean(Pre_Weight_g),
            meanWtPost = mean(Post_Weight_g),
            meandeltaWt = mean(deltaWt),
            n = n(),
            sddeltaWt = sd(deltaWt),
            sedeltaWt = sddeltaWt/sqrt(n),
            meanchangeWt = mean(changeWt*100),
            sdchangeWt = sd(changeWt),
            sechangeWt = sdchangeWt/sqrt(n),
            meandeltaFL = mean(deltaFL),
            sddeltaFL = sd(deltaFL),
            sedeltaFL = sddeltaFL/sqrt(n),
            meanchangeFL =mean(changeFL*100),
            sechangeFL = sd(changeFL)/sqrt(n),
            meanCFPre = mean(Pre_CF),
            meanCFPost = mean(Post_CF),
            seCF = sd(Pre_CF)/sqrt(n),
            meandeltaCF = mean(Delta_CF),
            sedeltaCF = sd(Delta_CF)/sqrt(n))
```

@@

Summary Stats
```{r}
Cage_only_DWSC %>%
 summarize(meanWtPre = mean(Pre_Weight_g),
            meanWtPost = mean(Post_Weight_g),
            meandeltaWt = mean(deltaWt),
            n = n(),
            sddeltaWt = sd(deltaWt),
            sedeltaWt = sddeltaWt/sqrt(n),
            meanchangeWt = mean(changeWt*100),
            sdchangeWt = sd(changeWt),
            sechangeWt = sdchangeWt/sqrt(n),
            meandeltaFL = mean(deltaFL),
            sddeltaFL = sd(deltaFL),
            sedeltaFL = sddeltaFL/sqrt(n),
            meanchangeFL =mean(changeFL*100),
            sechangeFL = sd(changeFL)/sqrt(n),
            meanCFPre = mean(Pre_CF),
            meanCFPost = mean(Post_CF),
            seCF = sd(Pre_CF)/sqrt(n),
            meandeltaCF = mean(Delta_CF),
            sedeltaCF = sd(Delta_CF)/sqrt(n))
```

@@

Make length plot
```{r}
CageClean <- Cageonly2 %>% select(Site, Enclosure, Pre_FL_cm, Post_FL_cm, changeFL) %>%
  filter(!is.na(Pre_FL_cm)) %>%
  filter(!is.na(Post_FL_cm)) %>%
  filter(changeFL>-0.05)

CagePrePost <- gather(CageClean, PrePost,FL,Pre_FL_cm, Post_FL_cm)
CagePrePost$Site <- factor(CagePrePost$Site, levels = c("RV", "DWSC"))
CagePrePost$PrePost <- factor(CagePrePost$PrePost,
                              levels = c('Pre_FL_cm','Post_FL_cm'),ordered = TRUE)

MeanLengthplot<- ggplot(data=CagePrePost) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=FL,  fill = PrePost)) +
  facet_wrap(~Site) +
  labs(y = "Length (cm)") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)++
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "", labels = c("Pre-Deployment", "Post-Deployment")) +
  labs(y = "Fork Length (cm)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
    scale_y_continuous(breaks = seq(4,8,0.5)) + 
  theme_bw() + theme(axis.title.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
  #scale_fill_discrete(name = "", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanLengthplot
```

@@

MeanWeightplot<- ggplot(data=CagePrePostW) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=Weight1,  fill = PrePostW)) +
  facet_wrap(~Site) +
  labs(y = "Mean Weight (g)") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)+
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment"))+
  #palette="Dark2" 
   labs(y = "Weight (g)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
  scale_y_continuous(breaks = seq(0,3,0.5)) + 
  theme_bw() + theme(strip.text.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) + 
  #scale_fill_discrete(name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        axis.text = element_text(size = 16),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanWeightplot
```

@@

MeanKplot<- ggplot(data=CagePrePostK) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=K1,  fill = PrePostK)) +
  facet_wrap(~Site) +
  labs(y = "Mean K") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)+
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment"))+
  #palette="Dark2" 
   labs(y = expression(K~(g~cm^-3)), x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
  theme_bw() + theme(strip.text.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) + 
  #scale_fill_discrete(name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanKplot
```

@@

Export
```{r}
tiff(filename=file.path("smelt_2019_winterspring/figures/WeightLengthKPlot.tiff"), units="in",type="cairo", bg="white", height=7.5, 
     width=7, res=300, pointsize=12,compression="lzw")
lwkplot
dev.off()
```
